Query Optimization for Dynamic Imputation

### 2017-05-08 paper/examples.tex
small paragraph on time-bound approach

>>>>

An alternative strategy involves starting with $\alpha=1$ and iterating to lower values, as long as execution
of the query completes within some user-defined time bound. \ProjectName{}'s planning
algorithm can expose the final set of plans that tradeoff execution time and imputation quality, which allows
the user to adjust their choice of $\alpha$ to uniquely select amongst these plans.
